### 2021-04-12 treatise-context/3_2_generating_beamforming_matrices.tex
Dimension of Fourier matrix

We argue as follows.
If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then
\DispNum {G:G:Ud:dU} {
\NC \M {G}
=\NC \M {U} \Rm {diag} \SB {\V {d}'} \M {U} ^\Adj \NR
}
for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}}.
Clearly,
\DispNum {G:2:g2:g2} {
\NC \VNm {\M {G}} _2
\NC =\VNm {\Rm {abs} \SB {\V {g}}} _2 \NR
}
where \m {\Rm {abs}} denotes entrywise absolute value.
Then if we notice that \m {\M {W} _B \M {W} _R \M {K} \M {U}} and \m {\M {U} ^\Adj \M {K}^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
\DispNum {W:2:WB:d's} {
\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U} \D
   \Rm {diag} \SB {\Rm {abs} \SB {\V {d}'}} \D
   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}'}} \D
   \R {\Rm {abs} \SB {\V {d}'}}
   \M {U} ^\Adj \M {K} ^\Adj \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\Adj \M {F} _R ^\Adj \M {K} \M {U}
   \R {\Rm {abs} \SB {\V {d}'}}} _2 \NR
%
\NC \eqsim \NC \VNm {\M {G}} _2 \RB {1 +2\d_s} \NR
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \Rf {H:H:l0:ql}.

>>>>

We argue as follows.
If angles \m {\th_l} (respectively \m {\f_l}) are exactly the multiples of \m {2 \pi / N_{H,t}} (respectively \m {2 \pi / N_{H,r}}), then
\DispNum {G:G:Ud:dU} {
\NC \M {G}
=\NC \M {U} \Rm {diag} \SB {\V {d}'} \M {U} ^\Adj \NR
}
for some \m {S}-sparse \m {\V {d}'} and unitary \m {\M {U}}.
Clearly,
\DispNum {G:2:g2:g2} {
\NC \VNm {\M {G}} _2
\NC =\VNm {\Rm {abs} \SB {\V {g}}} _2 \NR
}
where \m {\Rm {abs}} denotes entrywise absolute value.
Then if we notice that \m {\M {W} _B \M {W} _R \M {K} _r \M {U}} and \m {\M {U} ^\Adj \M {K} _t ^\Adj \M {F} _R^\Adj \M {F} _B^\Adj} has \m {\d_s} RIP too, we see
\DispNum {W:2:WB:d's} {
\NC \NC \VNm {\M {W} _B \M {W} _R \M {H} \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U} \D
   \Rm {diag} \SB {\Rm {abs} \SB {\V {d}'}} \D
   \M {U} ^\Adj \M {K} _t ^\Adj \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U}
   \R {\Rm {abs} \SB {\V {d}'}} \D
   \R {\Rm {abs} \SB {\V {d}'}}
   \M {U} ^\Adj \M {K} _t ^\Adj \M {F} _R \M {F} _B} _2 \NR
%
\NC =\NC \VNm {
   \M {W} _B \M {W} _R \M {K} _r \M {U}
   \R {\Rm {abs} \SB {\V {d}'}}} _2 \D
   \VNm {\M {F} _B ^\Adj \M {F} _R ^\Adj \M {K} _t \M {U}
   \R {\Rm {abs} \SB {\V {d}'}}} _2 \NR
%
\NC \eqsim \NC \VNm {\M {G}} _2 \RB {1 +2\d_s} \NR
}
Thus, even we cannot make sure that \m {\M {P}} is \m {\d_s} RIP with respect to all possible \m {\V {g}}'s, at least \m {\M {P}} has RIP with respect to relevant values of \m {\V {g}} according to the form \Rf {H:H:l0:ql}.

### 2021-04-12 treatise-context/5_conclusion.tex
Dimension of Fourier matrix

We corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
In particular, when the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
Therefore, one may use DS in the scenario that precision is crucial, as well as the case that the number of RF chains is more limited or fewer stages of estimation are possible.

>>>>

Since we have RIP, a whole series of compressive sensing techniques become possible.
But moreover, we corroborate the prediction that DS gives better regularization, and it may extract more information than other methods do when the sampling rate is low.
In particular, when the sample is less abundant and the noise level is higher, sometimes only DS can recover successfully.
Therefore, one may use DS for sake of higher precision, or with limited RF chains and fewer stages of estimation, for example, in the ultra reliable or low latency scenario.

### 2021-04-12 treatise-pdflatex/4_simulation.tex
Dimension of Fourier matrix

\Result
{Algorithm}
{
\begin {itemize}
\item Input \m {\M {P} \in \mathbb {C} ^{N_B^2 \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
%
\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \eqref {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
\leftarrow \begin {cases}
   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  & \IP {\V {1}, \tilde {\V {f}}'} \\
   \mathrm {subject} \; \mathrm {to} & \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   & - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   & \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
   & - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
\end {cases} 
}
\item Convert
%
\DispNum {g:::R1:1g} {
\Hat{\V {g}}
\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} 
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\hat {G}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} 
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\hat {\M {H}}
\leftarrow \M {K} \hat {\M {G}} \M {K}^\dagger 
}
\item Output \m {\hat {\M {H}}}.
\end {itemize}
}

@@

Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
We set \m {\g_{\mathrm {DS}} = 2 \R {2 \log \RB {N_{H,t} N_{H,r}}}} as suggested in \cite {CaT07}.
For sake of comparison, \m {\g_{\mathrm {Lasso}} = \g_{\mathrm {DS}}}.

@@

In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
We fix \m {N_R = \RB {3/2} N_B}.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-wide-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-tall-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-wide-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-tall-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
\end {figure}

@@

In the following, we plot for \m {N_Y = N_R = 4}, for different ratios of \m {N_{H,t}, N_{H,r}}.
%
\begin {figure} [H]
\includegraphics {error-medium-equal-square-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 8, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics {error-medium-equal-tall-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}externalfigure
%
\begin {figure} [H]
\includegraphics {error-medium-equal-wide-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}

@@

In the following, we plot for \m {N_B = 4}, for different number of stages.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
\end {figure}

@@

In the following, we plot for different thresholds, for \m {N_B = 4}, focusing on each of OMP, Lasso, DS.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}

@@

When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B} with \m {6} stages.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}

@@

Differing thresholds does not to seem have much effect on OMP and DS.
But for Lasso, a tighter threshold may result in a better estimation, but it may also blow up for high signal cases.
Increasing the number of stages obviously improves the estimation for all methods, and the main observation still applies.

>>>>

\Result
{Algorithm}
{
\begin {itemize}
\item Input \m {\M {P} \in \mathbb {C} ^{N_B^2 \D N_{H,t} N_{H,r}}}, \m {\V {y} \in \mathbb {C} ^{N_B^2}}, \m {\g_{\mathrm {DS}} > 0}.
%
\item Define \m {\tilde {\V {y}}, \tilde {\V {g}}, \tilde {\M {P}}, \tilde {\M {P}} ^\Adj, \tilde {\V {z}}}, according to \eqref {y:y:Ry:Ny}.
%
\item Compute the convex program
\DispNum {g:f:gf:S1} {
\hat {\tilde {\V {g}}}, \hat {\tilde {\V {f}}}
\leftarrow \begin {cases}
   \Min {\tilde {\V {g}}', \tilde {\V {f}}'}  & \IP {\V {1}, \tilde {\V {f}}'} \\
   \mathrm {subject} \; \mathrm {to} & \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   & - \tilde {\V {g}}' \preceq \tilde {\V {f}}' \\
   & \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
   & - \tilde {\M {P}}^\dagger \tilde {\M {P}} \tilde {\V {g}}' \preceq - \tilde {\M {P}}^\dagger \tilde {\V {y}} + \g_{\mathsf {DS}} \V {1} \\
\end {cases} 
}
\item Convert
%
\DispNum {g:::R1:1g} {
\Hat{\V {g}}
\leftarrow \mathcal {R} ^{-1} \SB {\Hat{\T{\V {g}}}} 
}
\item Calculate
%
\DispNum {G:G:ve:1g} {
\hat {G}
\leftarrow \mathrm {vec}^{-1} \SB {\hat {g}} 
}
\item Calculate
%
\DispNum {H:H:KG:GK} {
\hat {\M {H}}
\leftarrow \M {K} _r \hat {\M {G}} \M {K}^\dagger _t
}
\item Output \m {\hat {\M {H}}}.
\end {itemize}
}

@@

Denote the threshold for DS to be \m {\g_{\mathrm {DS}}}, and similar threshold of Lasso to be \m {\g_{\mathrm {Lasso}}}.
We set \m {\g_{\mathrm {DS}} = 2 \log \RB {N_{H,t} N_{H,r}}} as suggested in \cite {CaT07}.
For sake of comparison, \m {\g_{\mathrm {Lasso}} = \g_{\mathrm {DS}}}.

@@

In the following, we plot for different values and ratios of \m {N_B, N_{H,t}, N_{H,r}}.
We fix \m {N_R = \RB {3/2} N_B}.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-wide-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 8, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-small-more-tall-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-wide-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 24, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-big-more-tall-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 24}, with \m {6} stages, error.}
\end {figure}

@@

In the following, we plot for \m {N_Y = N_R = 4}, for different ratios of \m {N_{H,t}, N_{H,r}}.
%
\begin {figure} [H]
\includegraphics {error-medium-equal-square-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 8, N_{H,r} = 8}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics {error-medium-equal-wide-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics {error-medium-equal-tall-six-usual.png}
\caption {\m {N_B = 4, N_R = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, error.}
\end {figure}externalfigure

@@

In the following, we plot for \m {N_B = 4}, for different number of stages \m {3} and \m {9}.
We fix \m {N_R = \RB {3/2} N_B} with \m {6} stages again and in the below.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-three-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {3} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {9} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-nine-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {9} stages, error.}
\end {figure}

@@

In the following, we plot for different thresholds, for \m {N_B = 4}, focusing on each of OMP, Lasso, DS.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-oommpp.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of OMP, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-lasso.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of Lasso, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-square-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-wide-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 16, N_{H,r} = 12}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {error-medium-more-tall-six-ddss.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 16}, with \m {6} stages, different thresholds of DS, error.}
\end {figure}

@@

When plotting runtime statistics, we only consider the cases where \m {N_{H,t} = N_{H,r} = 3 N_B} with \m {6} stages.
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-small-more-square-six-usual.png}
\caption {\m {N_B = 2, N_{H,t} = 6, N_{H,r} = 6}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-medium-more-square-six-usual.png}
\caption {\m {N_B = 4, N_{H,t} = 12, N_{H,r} = 12}, with \m {6} stages, error.}
\end {figure}
%
\begin {figure} [H]
\includegraphics [width = \textwidth] {time-big-more-square-six-usual.png}
\caption {\m {N_B = 6, N_{H,t} = 18, N_{H,r} = 18}, with \m {6} stages, error.}
\end {figure}

@@

Differing thresholds does not to seem have much effect on OMP and DS.
Except for Lasso, where a tighter threshold may improve the accuracy, but a overtly tight threshold may also result in a blow up for high signal cases.
Increasing the number of stages obviously improves the estimation for all methods, and the main observation still applies.
